Analyzing DECREASE trials for extent of data fabrication

### 2017-02-01 submission/manuscript.tex
Interim commit

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Analyzing DECREASE trials for extent of data fabrication},
            pdfauthor={Chris HJ Hartgerink, Gerben ter Riet, Marleen Kemper},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\ImportTok}[1]{{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{{#1}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{{#1}}}}
\newcommand{\BuiltInTok}[1]{{#1}}
\newcommand{\ExtensionTok}[1]{{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Analyzing DECREASE trials for extent of data fabrication}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Chris HJ Hartgerink, Gerben ter Riet, Marleen Kemper}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{26 January, 2017}

@@

\caption{Test}\label{fig:figure 3}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res_i_certain}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##   [1] 0.1507 0.1624 0.1700 0.1674 0.1792 0.1807 0.1868 0.1867 0.1879 0.1930
##  [11] 0.2012 0.2182 0.2083 0.2114 0.2257 0.2296 0.2361 0.2476 0.2377 0.2488
##  [21] 0.2545 0.2631 0.2742 0.2788 0.2823 0.2894 0.3002 0.2996 0.3032 0.3094
##  [31] 0.3180 0.3243 0.3305 0.3352 0.3380 0.3547 0.3575 0.3649 0.3740 0.3873
##  [41] 0.3852 0.3957 0.4099 0.4088 0.4113 0.4205 0.4314 0.4378 0.4430 0.4524
##  [51] 0.4643 0.4655 0.4651 0.4851 0.4983 0.4931 0.5006 0.5106 0.5148 0.5241
##  [61] 0.5338 0.5428 0.5528 0.5549 0.5558 0.5768 0.5752 0.5797 0.5912 0.6043
##  [71] 0.6060 0.6177 0.6243 0.6283 0.6346 0.6433 0.6515 0.6586 0.6667 0.6684
##  [81] 0.6787 0.6895 0.6947 0.6978 0.7021 0.7121 0.7150 0.7264 0.7287 0.7402
##  [91] 0.7401 0.7522 0.7506 0.7533 0.7591 0.7762 0.7832 0.7782 0.7821 0.7873
## [101] 0.7894 0.7925 0.8009 0.8095 0.8175 0.8135 0.8211 0.8251 0.8306 0.8363
## [111] 0.8349 0.8372 0.8453
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res_i_uncertain}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##   [1] 0.1224 0.1247 0.1263 0.1213 0.1224 0.1318 0.1288 0.1355 0.1370 0.1419
##  [11] 0.1502 0.1448 0.1557 0.1582 0.1619 0.1730 0.1801 0.1758 0.1796 0.1869
##  [21] 0.1938 0.1968 0.2086 0.2106 0.2239 0.2267 0.2350 0.2414 0.2446 0.2602
##  [31] 0.2619 0.2716 0.2697 0.2896 0.3045 0.3067 0.3302 0.3313 0.3332 0.3543
##  [41] 0.3552 0.3801 0.3755 0.3816 0.4068 0.4056 0.4106 0.4231 0.4297 0.4384
##  [51] 0.4573 0.4694 0.4742 0.4911 0.4864 0.5000 0.5125 0.5172 0.5247 0.5337
##  [61] 0.5451 0.5518 0.5554 0.5640 0.5666 0.5798 0.5924 0.5896 0.6015 0.6100
##  [71] 0.6154 0.6297 0.6251 0.6376 0.6446 0.6480 0.6616 0.6649 0.6725 0.6786
##  [81] 0.6887 0.6913 0.6999 0.7077 0.7116 0.7248 0.7153 0.7227 0.7302 0.7379
##  [91] 0.7432 0.7499 0.7534 0.7530 0.7567 0.7708 0.7712 0.7762 0.7723 0.7988
## [101] 0.7908 0.7958 0.7998 0.8060 0.8082 0.8051 0.8234 0.8162 0.8240 0.8323
## [111] 0.8445 0.8647 0.8862
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res_iv_certain}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##    [1] 0.0223 0.0255 0.0234 0.0240 0.0263 0.0263 0.0226 0.0232 0.0220
##   [10] 0.0234 0.0251 0.0254 0.0247 0.0234 0.0276 0.0249 0.0268 0.0244
##   [19] 0.0244 0.0275 0.0264 0.0267 0.0267 0.0250 0.0279 0.0253 0.0254
##   [28] 0.0268 0.0267 0.0267 0.0267 0.0257 0.0264 0.0279 0.0264 0.0274
##   [37] 0.0285 0.0295 0.0269 0.0290 0.0301 0.0305 0.0288 0.0281 0.0271
##   [46] 0.0293 0.0280 0.0271 0.0266 0.0289 0.0283 0.0277 0.0299 0.0283
##   [55] 0.0296 0.0326 0.0344 0.0291 0.0321 0.0299 0.0287 0.0302 0.0289
##   [64] 0.0301 0.0297 0.0312 0.0315 0.0291 0.0308 0.0300 0.0298 0.0319
##   [73] 0.0283 0.0339 0.0311 0.0317 0.0313 0.0322 0.0324 0.0342 0.0302
##   [82] 0.0334 0.0332 0.0340 0.0334 0.0328 0.0349 0.0334 0.0348 0.0339
##   [91] 0.0339 0.0326 0.0350 0.0324 0.0353 0.0307 0.0339 0.0386 0.0379
##  [100] 0.0343 0.0347 0.0356 0.0370 0.0358 0.0343 0.0345 0.0356 0.0373
##  [109] 0.0399 0.0382 0.0376 0.0372 0.0376 0.0383 0.0374 0.0391 0.0349
##  [118] 0.0389 0.0377 0.0406 0.0443 0.0394 0.0402 0.0415 0.0406 0.0415
##  [127] 0.0412 0.0433 0.0430 0.0376 0.0399 0.0444 0.0418 0.0445 0.0464
##  [136] 0.0450 0.0461 0.0421 0.0447 0.0398 0.0418 0.0440 0.0461 0.0463
##  [145] 0.0500 0.0447 0.0438 0.0439 0.0492 0.0465 0.0464 0.0466 0.0487
##  [154] 0.0482 0.0467 0.0530 0.0501 0.0466 0.0510 0.0470 0.0540 0.0517
##  [163] 0.0542 0.0523 0.0549 0.0488 0.0509 0.0550 0.0550 0.0525 0.0541
##  [172] 0.0522 0.0579 0.0551 0.0548 0.0533 0.0590 0.0573 0.0557 0.0572
##  [181] 0.0548 0.0531 0.0598 0.0566 0.0613 0.0595 0.0599 0.0545 0.0627
##  [190] 0.0581 0.0625 0.0603 0.0643 0.0595 0.0650 0.0621 0.0657 0.0673
##  [199] 0.0648 0.0666 0.0684 0.0676 0.0654 0.0673 0.0679 0.0702 0.0687
##  [208] 0.0749 0.0713 0.0731 0.0696 0.0709 0.0702 0.0719 0.0764 0.0758
##  [217] 0.0733 0.0790 0.0725 0.0773 0.0770 0.0765 0.0778 0.0822 0.0789
##  [226] 0.0801 0.0814 0.0858 0.0820 0.0821 0.0854 0.0803 0.0824 0.0831
##  [235] 0.0864 0.0895 0.0845 0.0943 0.0883 0.0963 0.0930 0.0919 0.0871
##  [244] 0.0921 0.0940 0.0896 0.0967 0.0941 0.1000 0.0969 0.0980 0.0951
##  [253] 0.0988 0.1051 0.1031 0.1013 0.1059 0.0974 0.1055 0.1064 0.1074
##  [262] 0.1058 0.1068 0.1064 0.1117 0.1100 0.1069 0.1174 0.1078 0.1120
##  [271] 0.1107 0.1124 0.1180 0.1165 0.1190 0.1238 0.1187 0.1207 0.1219
##  [280] 0.1310 0.1247 0.1233 0.1288 0.1228 0.1319 0.1248 0.1337 0.1326
##  [289] 0.1339 0.1346 0.1329 0.1365 0.1366 0.1443 0.1395 0.1391 0.1377
##  [298] 0.1433 0.1424 0.1435 0.1466 0.1503 0.1519 0.1494 0.1459 0.1519
##  [307] 0.1578 0.1559 0.1500 0.1585 0.1550 0.1520 0.1651 0.1632 0.1662
##  [316] 0.1605 0.1623 0.1672 0.1663 0.1654 0.1730 0.1665 0.1721 0.1663
##  [325] 0.1789 0.1690 0.1754 0.1792 0.1782 0.1825 0.1827 0.1846 0.1820
##  [334] 0.1861 0.1884 0.1893 0.1936 0.1931 0.1956 0.1903 0.1942 0.1914
##  [343] 0.1901 0.2079 0.2054 0.2033 0.1976 0.2029 0.2099 0.2079 0.2084
##  [352] 0.2212 0.2063 0.2079 0.2232 0.2101 0.2222 0.2166 0.2184 0.2144
##  [361] 0.2220 0.2219 0.2351 0.2272 0.2271 0.2311 0.2337 0.2291 0.2382
##  [370] 0.2409 0.2362 0.2391 0.2327 0.2468 0.2372 0.2416 0.2520 0.2460
##  [379] 0.2548 0.2598 0.2457 0.2585 0.2620 0.2636 0.2608 0.2623 0.2661
##  [388] 0.2669 0.2655 0.2664 0.2662 0.2679 0.2702 0.2770 0.2752 0.2769
##  [397] 0.2836 0.2842 0.2828 0.2806 0.2860 0.2825 0.2788 0.2874 0.2987
##  [406] 0.2879 0.2975 0.2895 0.2920 0.3043 0.3040 0.3044 0.3065 0.3083
##  [415] 0.3066 0.3182 0.3098 0.3150 0.3167 0.3066 0.3137 0.3200 0.3153
##  [424] 0.3271 0.3237 0.3273 0.3252 0.3359 0.3381 0.3298 0.3320 0.3384
##  [433] 0.3328 0.3353 0.3417 0.3377 0.3521 0.3491 0.3432 0.3503 0.3540
##  [442] 0.3581 0.3569 0.3499 0.3632 0.3561 0.3652 0.3658 0.3703 0.3630
##  [451] 0.3637 0.3745 0.3743 0.3858 0.3751 0.3728 0.3801 0.3978 0.3775
##  [460] 0.3776 0.3882 0.3847 0.3893 0.3876 0.3899 0.3889 0.3906 0.3921
##  [469] 0.4023 0.4096 0.4099 0.4129 0.4029 0.4086 0.4096 0.4102 0.4108
##  [478] 0.4269 0.4119 0.4128 0.4277 0.4196 0.4194 0.4236 0.4307 0.4253
##  [487] 0.4279 0.4335 0.4413 0.4325 0.4449 0.4420 0.4371 0.4446 0.4488
##  [496] 0.4494 0.4533 0.4548 0.4574 0.4723 0.4585 0.4768 0.4649 0.4670
##  [505] 0.4617 0.4672 0.4727 0.4755 0.4753 0.4681 0.4862 0.4814 0.4835
##  [514] 0.4873 0.4832 0.4794 0.4749 0.4809 0.4973 0.4886 0.4986 0.4971
##  [523] 0.5020 0.4994 0.5077 0.5026 0.5016 0.5028 0.5094 0.5111 0.5157
##  [532] 0.5163 0.5252 0.5159 0.5145 0.5301 0.5237 0.5264 0.5364 0.5265
##  [541] 0.5337 0.5342 0.5420 0.5380 0.5473 0.5335 0.5496 0.5520 0.5463
##  [550] 0.5514 0.5471 0.5465 0.5572 0.5573 0.5569 0.5582 0.5618 0.5581
##  [559] 0.5711 0.5598 0.5705 0.5692 0.5758 0.5841 0.5741 0.5778 0.5785
##  [568] 0.5856 0.5898 0.5809 0.5956 0.5882 0.5916 0.6016 0.5906 0.5955
##  [577] 0.6025 0.6019 0.5995 0.5995 0.6165 0.6099 0.6058 0.6030 0.6195
##  [586] 0.6180 0.6142 0.6274 0.6210 0.6202 0.6308 0.6285 0.6253 0.6296
##  [595] 0.6348 0.6360 0.6446 0.6328 0.6408 0.6404 0.6390 0.6490 0.6529
##  [604] 0.6408 0.6524 0.6547 0.6440 0.6573 0.6582 0.6538 0.6579 0.6646
##  [613] 0.6699 0.6688 0.6707 0.6745 0.6714 0.6767 0.6739 0.6773 0.6863
##  [622] 0.6772 0.6827 0.6887 0.6903 0.6890 0.6941 0.7070 0.6965 0.6978
##  [631] 0.7017 0.7021 0.7107 0.6981 0.7082 0.7076 0.7137 0.7035 0.7197
##  [640] 0.7202 0.7168 0.7055 0.7230 0.7291 0.7289 0.7301 0.7281 0.7277
##  [649] 0.7348 0.7312 0.7336 0.7395 0.7424 0.7412 0.7415 0.7463 0.7491
##  [658] 0.7462 0.7457 0.7517 0.7573 0.7553 0.7580 0.7545 0.7525 0.7570
##  [667] 0.7567 0.7598 0.7663 0.7682 0.7717 0.7640 0.7707 0.7705 0.7758
##  [676] 0.7772 0.7756 0.7817 0.7779 0.7849 0.7966 0.7825 0.7862 0.7937
##  [685] 0.7902 0.7972 0.7933 0.7858 0.7964 0.7949 0.7984 0.8011 0.7970
##  [694] 0.8021 0.8076 0.8037 0.8106 0.8091 0.8119 0.8136 0.8124 0.8093
##  [703] 0.8086 0.8218 0.8195 0.8156 0.8202 0.8175 0.8287 0.8196 0.8284
##  [712] 0.8299 0.8276 0.8316 0.8237 0.8336 0.8291 0.8418 0.8362 0.8353
##  [721] 0.8376 0.8431 0.8465 0.8381 0.8416 0.8450 0.8416 0.8426 0.8440
##  [730] 0.8507 0.8440 0.8547 0.8493 0.8567 0.8528 0.8445 0.8588 0.8619
##  [739] 0.8548 0.8633 0.8534 0.8626 0.8626 0.8691 0.8658 0.8619 0.8686
##  [748] 0.8607 0.8693 0.8702 0.8726 0.8731 0.8749 0.8682 0.8763 0.8730
##  [757] 0.8717 0.8712 0.8751 0.8813 0.8830 0.8812 0.8811 0.8749 0.8830
##  [766] 0.8878 0.8838 0.8891 0.8871 0.8890 0.8866 0.8868 0.8898 0.8901
##  [775] 0.8863 0.8902 0.8962 0.8903 0.8947 0.8978 0.8944 0.8937 0.8985
##  [784] 0.9033 0.8936 0.8980 0.8984 0.9069 0.9011 0.8996 0.8956 0.9031
##  [793] 0.9007 0.8993 0.9015 0.9057 0.9060 0.9110 0.9130 0.9038 0.9040
##  [802] 0.9148 0.9115 0.9110 0.9132 0.9139 0.9179 0.9140 0.9089 0.9152
##  [811] 0.9162 0.9185 0.9105 0.9173 0.9160 0.9187 0.9176 0.9189 0.9184
##  [820] 0.9203 0.9191 0.9229 0.9214 0.9153 0.9251 0.9215 0.9259 0.9267
##  [829] 0.9177 0.9222 0.9312 0.9247 0.9366 0.9263 0.9303 0.9284 0.9276
##  [838] 0.9307 0.9288 0.9293 0.9293 0.9359 0.9324 0.9297 0.9346 0.9323
##  [847] 0.9352 0.9317 0.9365 0.9337 0.9354 0.9308 0.9316 0.9351 0.9386
##  [856] 0.9377 0.9344 0.9406 0.9388 0.9386 0.9362 0.9395 0.9396 0.9396
##  [865] 0.9381 0.9383 0.9376 0.9385 0.9422 0.9423 0.9404 0.9430 0.9417
##  [874] 0.9422 0.9380 0.9408 0.9443 0.9423 0.9462 0.9469 0.9467 0.9440
##  [883] 0.9466 0.9462 0.9533 0.9399 0.9487 0.9491 0.9492 0.9480 0.9446
##  [892] 0.9450 0.9462 0.9528 0.9501 0.9479 0.9495 0.9484 0.9501 0.9504
##  [901] 0.9486 0.9540 0.9497 0.9506 0.9538 0.9524 0.9517 0.9547 0.9528
##  [910] 0.9522 0.9551 0.9545 0.9558 0.9550 0.9537 0.9496 0.9515 0.9547
##  [919] 0.9542 0.9546 0.9520 0.9533 0.9557 0.9555 0.9530 0.9516 0.9603
##  [928] 0.9574 0.9584 0.9553 0.9574 0.9586 0.9584 0.9573 0.9540 0.9619
##  [937] 0.9597 0.9583 0.9554 0.9599 0.9586 0.9595 0.9598 0.9620 0.9625
##  [946] 0.9624 0.9638 0.9605 0.9597 0.9616 0.9631 0.9603 0.9644 0.9626
##  [955] 0.9598 0.9601 0.9647 0.9657 0.9643 0.9647 0.9619 0.9639 0.9644
##  [964] 0.9620 0.9635 0.9673 0.9666 0.9671 0.9658 0.9644 0.9648 0.9688
##  [973] 0.9643 0.9638 0.9624 0.9648 0.9658 0.9657 0.9673 0.9637 0.9679
##  [982] 0.9681 0.9678 0.9677 0.9683 0.9684 0.9658 0.9706 0.9703 0.9677
##  [991] 0.9661 0.9655 0.9676 0.9691 0.9698 0.9702 0.9675 0.9672 0.9725
## [1000] 0.9708 0.9704 0.9706 0.9707 0.9703 0.9679 0.9640 0.9719 0.9720
## [1009] 0.9712 0.9698 0.9710 0.9732 0.9711 0.9724 0.9704 0.9704 0.9698
## [1018] 0.9714 0.9717 0.9699 0.9720 0.9709 0.9748 0.9730 0.9718 0.9738
## [1027] 0.9721 0.9722 0.9709 0.9705 0.9683 0.9743 0.9737 0.9710 0.9735
## [1036] 0.9735 0.9758 0.9720 0.9747 0.9756 0.9686 0.9750 0.9740 0.9748
## [1045] 0.9740 0.9746 0.9752 0.9734 0.9760 0.9744 0.9736 0.9752 0.9767
## [1054] 0.9764 0.9734 0.9788 0.9773 0.9754 0.9750 0.9791 0.9791 0.9772
## [1063] 0.9789 0.9760 0.9789 0.9758 0.9777
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res_iv_uncertain}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##    [1] 0.0203 0.0200 0.0220 0.0211 0.0236 0.0200 0.0208 0.0193 0.0220
##   [10] 0.0222 0.0224 0.0228 0.0194 0.0218 0.0226 0.0221 0.0220 0.0210
##   [19] 0.0234 0.0216 0.0222 0.0242 0.0229 0.0254 0.0216 0.0225 0.0218
##   [28] 0.0224 0.0215 0.0221 0.0227 0.0221 0.0238 0.0233 0.0259 0.0243
##   [37] 0.0227 0.0255 0.0242 0.0216 0.0226 0.0210 0.0263 0.0218 0.0228
##   [46] 0.0232 0.0242 0.0214 0.0247 0.0252 0.0255 0.0240 0.0251 0.0252
##   [55] 0.0238 0.0246 0.0237 0.0265 0.0262 0.0272 0.0244 0.0262 0.0226
##   [64] 0.0245 0.0276 0.0243 0.0225 0.0251 0.0277 0.0297 0.0228 0.0263
##   [73] 0.0256 0.0274 0.0239 0.0259 0.0282 0.0287 0.0270 0.0267 0.0270
##   [82] 0.0265 0.0298 0.0298 0.0275 0.0285 0.0277 0.0278 0.0275 0.0269
##   [91] 0.0307 0.0260 0.0309 0.0273 0.0286 0.0292 0.0291 0.0334 0.0316
##  [100] 0.0297 0.0311 0.0299 0.0305 0.0296 0.0308 0.0303 0.0284 0.0297
##  [109] 0.0285 0.0274 0.0320 0.0287 0.0312 0.0306 0.0325 0.0300 0.0297
##  [118] 0.0306 0.0332 0.0333 0.0323 0.0319 0.0337 0.0306 0.0335 0.0354
##  [127] 0.0306 0.0338 0.0291 0.0314 0.0321 0.0346 0.0338 0.0365 0.0323
##  [136] 0.0327 0.0336 0.0341 0.0351 0.0372 0.0327 0.0319 0.0365 0.0321
##  [145] 0.0360 0.0339 0.0350 0.0364 0.0378 0.0344 0.0350 0.0362 0.0337
##  [154] 0.0364 0.0352 0.0348 0.0350 0.0355 0.0373 0.0383 0.0367 0.0369
##  [163] 0.0397 0.0360 0.0396 0.0432 0.0398 0.0409 0.0412 0.0438 0.0401
##  [172] 0.0407 0.0390 0.0422 0.0397 0.0434 0.0413 0.0418 0.0416 0.0410
##  [181] 0.0454 0.0402 0.0401 0.0429 0.0409 0.0427 0.0425 0.0461 0.0428
##  [190] 0.0479 0.0466 0.0436 0.0489 0.0464 0.0476 0.0469 0.0458 0.0454
##  [199] 0.0484 0.0445 0.0465 0.0466 0.0506 0.0487 0.0502 0.0494 0.0483
##  [208] 0.0483 0.0518 0.0550 0.0493 0.0508 0.0509 0.0535 0.0542 0.0502
##  [217] 0.0495 0.0510 0.0503 0.0486 0.0500 0.0530 0.0521 0.0534 0.0514
##  [226] 0.0545 0.0527 0.0581 0.0545 0.0619 0.0589 0.0595 0.0611 0.0572
##  [235] 0.0631 0.0582 0.0592 0.0607 0.0587 0.0571 0.0606 0.0600 0.0653
##  [244] 0.0645 0.0675 0.0614 0.0620 0.0682 0.0712 0.0648 0.0654 0.0677
##  [253] 0.0719 0.0650 0.0737 0.0692 0.0707 0.0736 0.0731 0.0748 0.0746
##  [262] 0.0789 0.0752 0.0760 0.0775 0.0749 0.0767 0.0753 0.0821 0.0847
##  [271] 0.0832 0.0814 0.0853 0.0878 0.0872 0.0870 0.0836 0.0862 0.0866
##  [280] 0.0869 0.0946 0.0909 0.0922 0.0960 0.0984 0.0901 0.0972 0.0955
##  [289] 0.1010 0.0977 0.0983 0.0986 0.1055 0.1048 0.1016 0.1065 0.1095
##  [298] 0.1046 0.1085 0.1134 0.1145 0.1135 0.1139 0.1188 0.1217 0.1133
##  [307] 0.1179 0.1158 0.1245 0.1229 0.1231 0.1235 0.1245 0.1212 0.1270
##  [316] 0.1278 0.1325 0.1304 0.1370 0.1337 0.1349 0.1355 0.1378 0.1432
##  [325] 0.1420 0.1479 0.1468 0.1422 0.1472 0.1499 0.1557 0.1567 0.1587
##  [334] 0.1564 0.1533 0.1631 0.1646 0.1596 0.1598 0.1548 0.1736 0.1659
##  [343] 0.1752 0.1718 0.1753 0.1759 0.1755 0.1795 0.1797 0.1881 0.1829
##  [352] 0.1843 0.1945 0.1868 0.1933 0.1931 0.1848 0.2012 0.1943 0.2025

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Analyzing DECREASE trials for extent of data fabrication},
            pdfauthor={Chris HJ Hartgerink, Gerben ter Riet, Marleen Kemper},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Analyzing DECREASE trials for extent of data fabrication}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Chris HJ Hartgerink, Gerben ter Riet, Marleen Kemper}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{01 February, 2017}

@@

\caption{Inversion method results used to estimate the number of data points fabricated in the DECREASE-I and DECREASE-IV trials. The top row panels indicate $p_F$ (y-axis) for all $X$ out of $N$ fabricated data points (x-axis). The bottom row indicates the estimated number of fabricated data points (y-axis) when varying the degree of confidence (x-axis). Dotted lines indicate the bounds for a 95 percent CI.}\label{fig:figure 3}
\end{figure}

For DECREASE-I, the 95\% confidence interval for the estimated number of
fabricated data points is {[}0 - 112{]} or {[}3 - 112{]} when based on a
point estimate or a more uncertain distribution estimate, respectively.
The left column of Figure 3 depicts the \(p_F\) per \emph{X} fabricated
data points (top panel) and the bounds of the confidence interval when
the degree of confidence is altered (lower panel). Staying clearly
between the dotted lines in the top panel, depicting the 95\% CI (top:
.975; bottom: .025), it becomes apparent that the degree of uncertainty
is too high to make any estimates with a high degree of confidence. This
due to the small sample size (i.e., \(N=112\)) combined with the
availability of just the summary results. Only when the degree of
confidence is lowered to around 75\% does the interval not span the
entire sample size. As such, based on the summary results, little can be
said about the extent of the data fabrication that occurred in the
DECREASE-I trial, affirming the conclusions of the original committee
report\textsuperscript{4}.

For DECREASE-IV, the 95\% confidence interval for the estimated number
of fabricated data points is {[}8 - 1059{]} or {[}7 - 1066{]} when based
on a point estimate or a more uncertain distribution estimate,
respectively. The minor difference between the estimates indicates that
there is a high degree of confidence that data fabrication did occur.
Nonetheless, the range of potentially fabricated data points is still
estimated at approximately 1000; this indicates that the summary results
are insufficient to provide more than an estimated lowerbound. However,
this does indicate that it is possible not all data were fabricated
(i.e., \(N=1066\)), increasing the importance of data provenance to
discern between genuine and falsified data. This affirms the conclusion
of the scientific integrity committee that the results of the
DECREASE-IV trial are ``scientifically incorrect''
(p.11)\textsuperscript{3}.

The results also highlight that, despite the lack of availability of raw
data, summary results from larger samples result in more certainty about
the estimated number of fabricated data points using the inversion
method. This is due to decreased standard errors at the population level
of the effects, providing less variation in the simulations and
resulting in higher sensitivity. However, this also highlights that in
order to prevent detection it would be in the fabricators' interest to
fabricate small studies (assuming the fabricator wants to remain
undetected).
